---
  output: github_document
---

[![Travis build status](https://travis-ci.com/muschellij2/talkr.svg?branch=master)](https://travis-ci.com/muschellij2/talkr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/talkr?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/talkr)
[![Coverage status](https://codecov.io/gh/muschellij2/talkr/branch/master/graph/badge.svg)](https://codecov.io/gh/muschellij2/talkr)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# talkr Package: 
The goal of `talkr` is to provide use natural language commands to talk through data analysis using `dplyr`.  Currently, natural language processing is not used but a simple grammar.

## Installation

You can install `talkr` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/talkr")
```

## Example

We will pass in a command to sort the data set.
```{r}
library(talkr)
library(tibble)
library(dplyr)
df = tibble::rownames_to_column(mtcars, var = "car")
is.unsorted(df$mpg)
res = df %>%
  talk("Sort df by mpg")
is.unsorted(res$mpg)
```



If you do not specify the order, it assumes ascending, as `dplyr::arrange` does:

```{r}
cmds = c(
  "Sort by mpg ascending and hp decreasing",
  "Sort by mpg and hp decreasing")
res = lapply(cmds, talk_arrange, .data = df)
all.equal(res[[1]], res[[2]])
```


## Shiny Example

Here is a Shiny app based on https://github.com/yihui/shiny-apps/tree/master/voice, which has an app here: https://yihui.shinyapps.io/voice/.  This uses the `annyang` API: https://github.com/TalAter/annyang.  See a live demo at https://jhubiostatistics.shinyapps.io/Speak_dplyr/

```{r, eval = FALSE}
talk_shiny_example("sort_better")
```
